Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-07-04 WSSSPE2_report/WSSSPE2_review.tex
Section 7.1.2: minor changes.

``How will we know when people are trained effectively in these new skills?'' We
discussed certification. It can be hard to build the recognition of Java or
database certifications amongst all technologies. OSS offers badges to those
completing training. However we need to demonstrate proficiency, not just
completion. Google Summer of Code is a big CV augmentation for
participants---can we create something similar?

@@

We then discussed variations amongst scientific domain areas and wondered ``Are
some communities more or less open than others?'' To some members of the group
biology seems to be open, while physics less so. Some felt with the more recent
development of bioinformatics as a field there were fewer historical practices
to undo. Physics has pre-print philosophy to overcome. Environmental sciences
may be mixed. The group felt the biomedical area, however, was very competitive
and closed. One participant mentioned blueprints for going open source (like
NWChem recently did) where authors outline how this helps, what you do and what
the next steps are.

>>>>

``How will we know when people are trained effectively in these new skills?'' We
discussed certification. It can be hard to build the recognition of Java or
database certifications among all technologies. OSS offers badges to those
completing training. However we need to demonstrate proficiency, not just
completion. Google Summer of Code is a big CV augmentation for
participants---can we create something similar?

@@

We then discussed variations among scientific domain areas and wondered ``Are
some communities more or less open than others?'' To some members of the group,
biology seems to be more open, while physics less so. Some felt, with the more recent
development of bioinformatics as a field, there were fewer historical practices
to undo in biology. Physics has preprint philosophy to overcome. Environmental sciences
may be mixed. The group felt that the biomedical area, however, was very competitive
and closed. One participant mentioned blueprints for going open source (like
NWChem recently did) where authors outline how this helps, what you do and what
the next steps are.
